Insights Into Computational Reproducibility in Plant Pathology and a Way Forward

### 2021-06-14 analysis/paper/paper.Rmd
Full stops after initials and clarify contributions further

A.H.S, E.DP, Z.F. and N.J.G. conceived of the presented idea and scoring system.
N.J.G. provided five-year impact factors.
A.H.S, E.DP, Z.F. and K.dSA evaluated articles for scoring.
A.H.S. designed the computational framework with feedback from E.DP and Z.F.
A.H.S wrote the manuscript in consultation with E.DP.
<!-- All authors provided critical feedback and helped contribute to the final version of the manuscript. -->

>>>>

A.H.S, E.DP., Z.F. and N.J.G. conceived of the presented idea and scoring system.
N.J.G. provided five-year impact factors.
A.H.S., E.DP., Z.F. and K.dSA. evaluated articles for scoring.
A.H.S. designed the computational framework for analysis and created the research compendium with feedback from E.DP. and Z.F.
A.H.S. wrote the manuscript in consultation with E.DP.
<!-- All authors provided critical feedback and helped contribute to the final version of the manuscript. -->
